Spin canonical rings of log stacky curves

### 2015-07-02 stacky_write_up/spin_cring.tex

There are two main cases: when $\delta \geq 2$ and when $\delta = 0$,
where we are implicitly appealing to Remark ~\ref{rem:delta-not-1}.
In the first case, $\deg \lfloor \halfcan \rfloor \geq 0$ so the
result directly follows from Lemma ~\ref{lem:sat-1}. When $\delta =
0$, the proof is a rather involved induction using Lemma
~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}. The
remainder of this section is dedicated to characterizing the
saturations (Subsection ~\ref{ssec:g_0_saturation}), inductive
base cases ( Subsection ~\ref{ssec:g_0_base}), and exceptional
cases (Subsection ~\ref{ssec:g-0-exceptional}) when $\delta = 0$
before proving the main theorem in full for all $\delta$ in
Subsection ~\ref{ssec:g-0-main}.

>>>>

As noted in Remark ~\ref{rem:delta-not-1}, $\delta$ is even, so we can reduce to two cases: $\delta \geq 2$ and $\delta = 0$.
In the former case, $\halfcan$ is linearly equivalent to an effective divisor, so the
result of Theorem \ref{thm:main} follows immediately by repeatedly applying Lemma ~\ref{lem:sat-1} to add the necessary fractional points.
On the other hand, the proof when $\delta =
0$ is a more involved, and we dedicate the remainder of this section to proving it through the following steps: 
characterizing saturations points (Subsection ~\ref{ssec:g_0_saturation}), describing
base cases (Subsection ~\ref{ssec:g_0_base}), presenting exceptional
cases (Subsection ~\ref{ssec:g-0-exceptional}), and applying inductive Lemmas ~\ref{lem:sat-3} and ~\ref{lem:raise-stacky-order} to prove \todo{synonym for prove, so its not repeated twice in this sentence?} Theorem \ref{thm:main} when $\delta = 0$ (Subsection ~\ref{ssec:g-0-main}.\todo{Peter: I made some changes to this last paragraph (gramatical and stylistic-not mathematical).  See if you like them.}
%before proving the main theorem in full for all $\delta$ in
%Subsection ~\ref{ssec:g-0-main}.
